---
title: "HFT 2025"
author: "Nihad & Vikram"
date: "`r Sys.Date()`"
editor: visual
date: "`r Sys.Date()`"
engine: knitr
format: 
  html:
    toc: true
    toc-depth: 3
    toc-location: left
    smooth-scroll: true
    toc-title: Contents
    tbl-cap-location: bottom
    lof: true
    lot: true
    theme: spacelab
    highlight: tango
    df-print: kable
    toc_float:
      collapsed: false
      smooth_scroll: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo    = TRUE, 
                      cache   = FALSE, #https://yihui.org/knitr/options/#cache
                      message = FALSE, 
                      warning = FALSE)
options(scipen = 10)
library(knitr)

```

## 1 Importing the data

First, let's load necessary libraries:

```{r cache = F}
library(xts)
library(quantmod)
library(chron)
library(urca) # for cointegration tests
library(TTR)
library(caTools)
library(lubridate)
library(lattice) # for levelplot()
library(grDevices)
library(dplyr) # for if_else()


```

Let's also load the additional function:

```{r}
source("https://raw.githubusercontent.com/ptwojcik/HFD/master/functions_plotHeatmap.R")

source("functions/load_and_pre_process.R")
source("functions/define_entry_exit.R")
source("functions/execute_strategies.R")
source("functions/define_daily_filters.R")
source("functions/execute_one_at_a_time.R")
```

## Approaches undertaken

This part should describe **in short** what particular methods you used, all entry/exit techniques considered, all additional assumptions.

For **each group of assets separately** You should also explain **WHAT different parameters** you considered (e.g. memories of moving averages, types of moving averages, types of volatility measures, memory of volatility measures, types of additional indicators, memories of additional indicators, etc.), what (if any) additional filtering rules you applied.

You should also explain with details **HOW** you searched for the best combination of parameters for a particular group of assets.

## Finally selected strategy for **group 1**

Provide a **general summary** (approach and a set of **final parameters**) for assets from **group 1**. (e.g. momentum strategy, cross over of two exponential moving averages EMA10 and EMA60).

